Thesis Draft

### 2015-10-13 chapter4.tex
puzzle notebook.
Former-commit-id: 9d9397215989fa8018a50262946fbe342928ce75

@@

\subsubsection{Name of notebooks}
\begin{itemize}
\item Puzzle, because it is cut out from very big and long banner (which is carried at graduation ceremony at METU). Every piece was a part of bigger banner. 
\item 12.00 pm. Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
\item ... because 
\item 08.00 am/gevrek, breakfast time. 
\end{itemize}

@@

>>>>

% Structure of chapter:
% 
% Artist Statement
% Work
% Exhibition

% \ldots is the concern of this study which aims to \ldots

% The aim is not to practice Antiquarian Avant-Garde techniques as a puritan form of photography, but rather to envision new means of photography.

@@

\subsubsection{Name of notebooks}
\begin{itemize}
\item Puzzle, because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011). Every piece was a part of bigger banner. At that time there are serious debates about freedom on the internet. Most of the website are banned from the decision to the courts and they were not accessible. (Access to this banner is blocked by a court decision.) In Middle East Technical University there is a tradition that in graduation ceremony people walk through in the stadium and greet to the tribunes. With this event they carry some banners to express their feelings and criticize some realities in the country. This one of them. It is carried by students (new grads of Computer Engineering) The slogan decided by among the students and before the ceremony I printed out the slogan to carried out as many people as it can and easy to readable from the people who seat at the tribunes. After the ceremony I could not throw away this banner. I do not know what to do it, it is very big actually to store but I could not. I think that I will figure out later. Maybe I can use it as a draft paper. But is it worth to cut out this all long banner etc. Also to strengthen the banner and to prevent to tear while carried by the many people we are tape it from its boundaries. In other words some of the areas can not approiate for writing. When I decided to this topic I remembered to this banner. It is stands in a corner in a dusty way. Now it is time use it. It waited very log time and it is time to revive again. Currently In turkey the problem of banning web-sites continues. Event it can said that people do not surprises when a website is blocked by the courts. It can be turn be a paper that people can freely express their ideas and feeling onto the it. Cut out them to the smaller pieces and make them as notebooks. They are part of puzzle. for the smaller parts what is written on them can not easily understandable. To realize what is the message is you have to bring together all of them again. But It is not possible, therefore website is a very good solution for them. All pages have unique patterns. Remaining parts of letter and tape. It provides unique layout for writing and I strongly think that all the notebooks after used have strong visual impact. 
\item 12.00 pm. Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
\item 08.00 am/gevrek, breakfast time. I think that these packages are used at the morning, very the beginning of the day.
\end{itemize}

@@

% Counter Argument:
% People may think and raise the question that none of notebooks is actually my work they belongs to others, others(Starbucks, Burger King) designed it and I am stealing their work. Here there are available different answers to the question. Firstly they are different once they are designed. Turned to different thing. I suggest that them to consider in different context like Duchamp.

% I resurrect things that have been killed off... My work is all about the potential of materials — even when it looks like they've lost all possibilities. (Cornelia Parker) https://en.wikipedia.org/wiki/Cornelia_Parker

% These all memories and collected materials related with the my history. So why is it important for the other people. What can they found my memories. This is not theirs. How other people connect to the topic. They important for me but also I need to find something important for the other people. For example modshifter and varuna gezgin is one of them. This not only my experience. Some kind of shared memories and histories. What will find people in these notebooks.

% Is it important that the place where people access them? How to design the experience here.
